Online {\IterComp}

### 2017-11-16 results.tex
minor results

Some benchmarks display unexpectedly higher overheads under the relaxation strategies. This is counter-intuitive because relaxation only
reduces the number of instrumented probes without changing their placement. By analyzing these cases, we noticed that we could not remove
the most frequently executed probes, so relaxation had little positive impact. At the same time, we removed some probes which were
infrequently executed but were taken into consideration by the LLVM optimization heuristics. In some cases, removed probes caused different
and suboptimal decisions to be made, increasing the runtime.

@@

In this section we evaluate the effectiveness of our work efficiency metric. We perform online {\itercomp} using all five profiling
strategies, namely \OracleRM, \OraclePP, \OptProf, \WCRelax-5\%, and \WPRelax-5\%. We evaluate every optimization sequence on multiple
inputs, using a dynamic input-window size, as explained in Section~\ref{sec:oic-infra}. We use the average work efficiency over the input
window to rank different optimization sequences and we select the one with the highest work efficiency.

>>>>

Some benchmarks display unexpectedly higher overheads under the relaxation strategies. This is counter-intuitive because relaxation only
reduces the number of instrumented probes without changing their placement. By analyzing these cases, we noticed that we could not remove
the most frequently executed probes, so relaxation had little positive impact. At the same time, we removed some probes which were
infrequently executed but were taken into consideration by the LLVM optimization heuristics. In some cases, removed probes caused different
and suboptimal decisions to be made, very slightly increasing the runtime.

@@

In this section we evaluate the effectiveness of our work efficiency metric. We perform online {\itercomp} using all five profiling
strategies, namely \OracleRM, \OraclePP, \OptProf, \WCRelax-5\%, and \WPRelax-5\%. We evaluate every optimization sequence on multiple
inputs. We use work efficiency to rank different optimization sequences and we select the one with the highest work efficiency.
